%-----------------------------------------------------------------------------------------------------------------------------------------------%
%	The MIT License (MIT)
%
%	Copyright (c) 2021 Jitin Nair
%-----------------------------------------------------------------------------------------------------------------------------------------------%

\documentclass[a4paper,12pt]{article}

%----------------------------------------------------------------------------------------
%	PACKAGES & OTHER CONFIGURATIONS
%----------------------------------------------------------------------------------------
\usepackage{url}
\usepackage{parskip} 	
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.9]{geometry}
\usepackage{tabularx}
\usepackage{enumitem}
\newcolumntype{C}{>{\centering\arraybackslash}X} 
\usepackage{supertabular}
\usepackage{titlesec}				
\usepackage{multicol}
\usepackage{multirow}

\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{10pt}

\usepackage[style=authoryear,sorting=ynt, maxbibnames=2]{biblatex}
\usepackage[unicode, draft=false]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}
\addbibresource{citations.bib}
\setlength\bibitemsep{1em}
\usepackage{fontawesome5}

% Disable hyphenation and ensure full justification for body text
\usepackage[none]{hyphenat}
\usepackage{ragged2e}
\hyphenpenalty=10000
\exhyphenpenalty=10000

% job listing environments
\newenvironment{jobshort}[2]
    {\begin{tabularx}{\linewidth}{@{}l X r@{}} \textbf{#1} & \hfill &  #2 \\[3.75pt] \end{tabularx}}
    {}

\newenvironment{joblong}[2]
    {\begin{tabularx}{\linewidth}{@{}l X r@{}} \textbf{#1} & \hfill &  #2 \\[3.75pt] \end{tabularx}
    \begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt,label=--]}
    {\end{itemize} \end{minipage}}

%----------------------------------------------------------------------------------------
%	BEGIN DOCUMENT
%----------------------------------------------------------------------------------------
\begin{document}
\pagestyle{empty} 
% Use full justification for document body (keeps words from being hyphenated)
\justifying

%----------------------------------------------------------------------------------------
%	TITLE / CONTACT INFO
%----------------------------------------------------------------------------------------
\begin{tabularx}{\linewidth}{@{} C @{}}
\Huge{Kevin Benny Mathew} \\[7.5pt]
\href{https://github.com/KevinBMathew}{\raisebox{-0.05\height}\faGithub\ KevinBMathew} \ $|$ \ 
\href{https://linkedin.com/in/kevin-mathew-672774249}{\raisebox{-0.05\height}\faLinkedin\ Kevin Mathew} \ $|$ \ 
\href{mailto:f20230143@goa.bits-pilani.ac.in}{\raisebox{-0.05\height}\faEnvelope \ f20230143@goa.bits-pilani.ac.in} \ $|$ \ 
\href{tel:+917776063339}{\raisebox{-0.05\height}\faMobile \ +91-7776063339} \\
\normalsize{A901, La Cresta, Sopan Baug, Ghorpadi, Pune, Maharashtra - 411001}
\end{tabularx}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
\section{Education}
\begin{tabularx}{\linewidth}{@{}l X r@{}}	
2023 - 2027 & B.E. (Hons.) Electronics and Communication Engineering - & \textbf{8.13/10} \\
& BITS Pilani, Goa Campus &  \textsuperscript{\textbf{(Upto Semester 4)}}\\
May 2023 & ISC (Class XII) - The Bishop's School, Camp & \textbf{97.6\%} \\
May 2021 & ICSE (Class X) - St. Mary's School, Pune & \textbf{99.0\%} \\
\end{tabularx}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE
%----------------------------------------------------------------------------------------
\section{Work Experience}
\begin{joblong}{Summer Intern}{May 2025 - Aug 2025}
\item Worked at the \textbf{Indian Meteorological Department} on sensor fusion and algorithm development.
\item Implemented custom fuzzy logic and Kalman filters for high-accuracy temperature sensing.
\item Developed embedded code for ESP8266 hardware using C++ and PlatformIO.
\item Conducted data analysis using Python and documented results for research publication.
\end{joblong}

%----------------------------------------------------------------------------------------
%	PROJECTS
%----------------------------------------------------------------------------------------
\section{Projects}

\begin{joblong}{Development of Flexible Tactile Sensors}{Dec 2025 - Present}
\item Currently in process of developing tactile sensors for robotic perception under Dr. Tushar Sakorikar.
\item Project is currently in literature review and ideation phase with plans to start fabrication by February 2026
\end{joblong}

\begin{joblong}{Low Cost Electromechanical Tensile Tester}{May 2025 - Dec 2025}
\item Developed a horizontal tensile tester for the characterization of soft materials under Dr. Tushar Sakorikar.
\item Executed end-to-end development including mechanical design, 3D modeling, and electronics architecture.
\item Integrated motion control using Teensy microcontrollers, stepper motors, and a custom UI.
\end{joblong}

\begin{joblong}{Project Vulcan: Humanoid Robot}{Feb 2024 - Present}
\item Led the bionic arm subsystem, developing a 7-DOF biomimetic robotic arm emulating human movement.
\item Improved internal mechanical systems for facial movements, specifically eyes and mouth.
\item Implemented amplifiers for microphones located in the robot's ears.
\end{joblong}

\begin{joblong}{Project Kratos: Mars Rover}{Aug 2024 - Present}
\item Core member of the electronics subsystem; migrated the code stack from ROS Noetic to ROS2 Humble.
\item Redesigned the electronics box for modularity, easier assembly, and improved debugging.
\item Designed custom mounts for cameras and sensors using Fusion 360.
\end{joblong}

\pagebreak
%----------------------------------------------------------------------------------------
%	POSITIONS OF RESPONSIBILITY / VOLUNTEERING
%----------------------------------------------------------------------------------------
\section{Leadership \& Volunteering}
\begin{jobshort}{Research Head - Electronics and Robotics Club (ERC), BITS Goa}{Apr 2025 - Present}
Managing project progress and integrating electronics, mechanical, and automation verticals.
\end{jobshort}

\begin{jobshort}{Committee Member - Sandbox Innovation Lab, BITS Goa}{Feb 2024 - Present}
Maintaining lab equipment (3D printers, laser cutters) and managing tech club purchases.
\end{jobshort}

\begin{jobshort}{Volunteer - Abhigyaan, BITS Goa}{Oct 2023 - Present}
Provided evening tuition classes for K-12 children of campus non-teaching staff.
\end{jobshort}

%----------------------------------------------------------------------------------------
%	SKILLS
%----------------------------------------------------------------------------------------
\section{Skills \& Proficiency}
\begin{tabularx}{\linewidth}{@{}l X@{}}
	\textbf{Languages} & C++, C, Python, Java, Verilog \\
	\textbf{Technologies} & ROS/ROS2, Git, Linux, Microcontrollers (ESP32, Arduino, Teensy, ESP8266) \\
	\textbf{Tools} & KiCAD, Fusion 360, Solidworks, Onshape, MATLAB, PlatformIO, Android Studio \\
	\textbf{Key Courses} & Control Systems, Microprocessors \& Interfacing, Digital Design, VLSI Design, Communication Systems, Digital Signal Processing \\
\end{tabularx}

\vfill
\center{\footnotesize Last updated: \today}
\end{document}